### 2013-08-16 Tex/chapters/conclusion.tex
Conclusion angepasst... muss wohl noch ausgebaut werden

In this thesis the properties of an Ising ferromagnet which nodes are
moved by a Gaussian distributed displacement is studied. The neighbor
relationship is provided by two proximity graphs -- the RNG and the GG.
The coupling constants are distance dependend. This model is within the
universality of the square lattice Ising ferromagnet. Its critical temperature
decreases with increasing disorder on a RNG. On a GG it first jumps,
increases up to a maximum and decreases after that. The course of the
critical temperatures can be made plausible observing the degree of the
underlying graph, but no explicit formular was found.

\subsection{Outlook}
    The behavior of the normalized critical temperatures in dependence
    on \(\sigma\) of the Relative Neighborhood graph and Gabriel graph
    are qualitative similar to each other. One could study the behavior
    of other proximity graphs like the minimum spanning tree or the
    Delaunay triangulation to examine if it is also similar.\\
    Also it would be interesting to compare this results with the
    results obtained by the same experiments with \(\alpha = 0\), which
    implies that the coupling constant is independent from the distance
    on the sites. That way the critical temperature would be more
    straight forward normalized by the degree of the graph. It
    could be determined if the qualitative similarities of the
    normalized temperatures over the disorder parameter of different
    graph types are related to the choice of the function determining the
    coupling constant.

>>>>

In this thesis the properties of an Ising ferromagnet, which nodes are
moved by a Gaussian distributed displacement, is studied with Monte Carlo
Simulations. The neighbor relationship is provided by two proximity graphs
-- the RNG and the GG. These graphs conserve the two dimensional character
of the lattice, because their edges do not cross. The coupling constants
are distance dependend, they are getting exponential weaker at higher distances.\\
This model is within the universality of the square lattice Ising
ferromagnet. Its critical temperature decreases with increasing disorder
on a RNG. On a GG it first jumps, increases up to a maximum and decreases
after that. At high disorder it approaches the limit of randomly generated
graphs of the respective type. The course of the critical temperatures
can be made plausible observing the degree of the underlying graph, but
no explicit formular was found.

\subsection{Outlook}
    The behavior of the normalized critical temperatures in dependence
    on \(\sigma\) of the Relative Neighborhood graph and Gabriel graph
    are qualitative similar to each other. One could study the behavior
    of other proximity graphs like the minimum spanning tree or the
    Delaunay triangulation to examine if it is also similar.\\
